Supplementary figures\nCapturing regeneration in models of forest dynamics

### 2023-04-26 manuscript/supplementaryRW.Rmd
updates in supplementary

We considered each of the $11$ species in the protocol explicitly. We
chose the model parameters for the individual species based on the work
by @bohn2014. For species that were not covered by @bohn2014, we used
parameter values of similar species with known parameters. The species
composition was not predefined and evolved solely from the seed input
and the model dynamics.

@@

zeroInflated <- readr::read_csv(here::here("data", "noRecruitment.csv"))
zeroInflated$Model[zeroInflated$Model == "Empirical"] <- "Observations"

>>>>

We considered each of the $11$ species in the protocol explicitly. We
chose the model parameters for the individual species based on the work
by Bohn et al (2014). For species that were not covered by Bohn et al
(2014), we used parameter values of similar species with known
parameters. The species composition was not predefined and evolved
solely from the seed input and the model dynamics.

@@

zeroInflated <- readr::read_csv(here::here("figures", "noRecruitment.csv"))
zeroInflated$Model[zeroInflated$Model == "Empirical"] <- "Observations"
